Radiance - A Web Application Environment

### 2016-12-21 els2017-radiance/paper.tex
Change address.
Minor crap.

\numberofauthors{1}
\author{
\alignauthor
Nicolas Hafner\\
       \affaddr{ETH Zürich}\\
       \affaddr{Rämistrasse 101}\\
       \affaddr{8092 Zürich, Switzerland}\\
       \email{shinmera@tymoon.eu}
}
\date{15 November 2016}

@@

\section{Introduction}
Most tasks involved in writing a website or web application are not very complex or complicated; they usually involve solving very similar problems every time. This trend lead to the rise of web frameworks-- collections of tools and libraries to take care of the most common of aspects for the developer. \\

@@

Radiance provides standard interface definitions for most of the common aspects of web application programming, allowing the sharing of the previously discussed common resources. However, it is also sensible to define interfaces for commonly needed tools that may have slightly different implementation details. An example for this would be a caching system; the exact behaviour of the cache can vary --be it database-backed, file-backed, memory-backed, etc.-- but the usage of the system is the same, regardless of implementation details. \\

@@

As it stands, Radiance would translate a request to \\\texttt{http://radiance.example.com/test/index} into the URI \\\texttt{radiance.example.com/test/index} and then map it to \\\texttt{radiance/test/index}. The top-level domain --the part of the domain we cannot change-- is stripped away by one of the standard routes. This URI is still not one that would invoke our page though. Therefore, additional routes need to be set up to handle the conversion to and from the internal representation.

>>>>

\numberofauthors{1}
\author{
\alignauthor
Nicolas Hafner\\
       \affaddr{Shirakumo.org}\\
       \affaddr{Zürich, Switzerland}\\
       \email{shinmera@tymoon.eu}
}
\date{15 November 2016}

@@

\section{Introduction}
Most tasks involved in writing a website or web application are not very complex or complicated; they usually involve solving very similar problems every time. This trend lead to the rise of web frameworks--- collections of tools and libraries to take care of the most common of aspects for the developer. \\

@@

Radiance provides standard interface definitions for most of the common aspects of web application programming, allowing the sharing of the previously discussed common resources. However, it is also sensible to define interfaces for commonly needed tools that may have slightly different implementation details. An example for this would be a caching system; the exact behaviour of the cache can vary ---be it database-backed, file-backed, memory-backed, etc.--- but the usage of the system is the same, regardless of implementation details. \\

@@

As it stands, Radiance would translate a request to \\\texttt{http://radiance.example.com/test/index} into the URI \\\texttt{radiance.example.com/test/index} and then map it to \\\texttt{radiance/test/index}. The top-level domain ---the part of the domain we cannot change--- is stripped away by one of the standard routes. This URI is still not one that would invoke our page though. Therefore, additional routes need to be set up to handle the conversion to and from the internal representation.
